Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-06-21 ms.tex
new figures illustrating 100 GHz spherical harmonic template correction
swapped out quadrupole equation/discussion with spherical harmonic decompositon equation/discussion

\begin{figure}
\begin{center}
\epsfig{file=dipole_all.eps, width=3.4in}
\caption{\label{fig:dip}  Scatter plots of \PLANCK~143, 217, 353, and 545 GHz 
versus \PLANCK~857 GHz. Left: before correcting for offset and residual Solar 
dipole. Right: after correcting or the best-fit offset and dipole amplitude, as
described in $\S$\ref{sec:zp}. The dashed red line shows the best-fit linear 
relationship in each case.}
\end{center}
\end{figure}

\begin{figure*}
\begin{center}
\epsfig{file=quad_100.eps, width=6.5in}
\caption{\label{fig:quad} Summary of low-order corrections at 100 GHz.}
\end{center}
\end{figure*}

@@

The need for additional low-order corrections beyond simple scalar offsets 
became evident upon inspecting the HFI maps at 100-545 GHz. In particular, we 
noticed the presence of a low-level dipole pattern, with an orientation 
consistent with that of the Solar dipole. Our strategy will be to 
simultaneously fit both the residual dipole and zero-level offset amplitudes. 
To most precisely recover these amplitudes, it is necessary to have the highest
available S/N in the independent variable of our regression. For this reason we
have used \PLANCK~857 GHz as a reference for the 100-545 GHz bands, as opposed 
to the FDS99 predictions or H\,\textsc{i} data. In doing so, we assume
\PLANCK~857 GHz contains no appreciable Solar dipole residual or other 
low-order problems. % grammar?

@@

For \PLANCK~100 GHz, we found an additional low-order correction to be
necessary (see Figure \ref{fig:quad}). Therefore, for 100 GHz, we performed a 
modified version of the Equation \ref{equ:dip} fit, using the following model:

\begin{equation} \label{equ:quad}
\mathcal{I}_{100, p} = m\mathcal{I}_{857, p} + b + d\mathcal{D}_p + qQ_p
\end{equation}

We will refer to the additional term $qQ_p$ as the ``quadrupole correction''. 
The shape of the quadrupole template is given by:

\begin{equation}
Q_p = cos^2(\theta_p)
\end{equation}

Where $\theta_p$ is the angle of pixel $p$ relative to the Solar velocity 
vector. It is not clear physically why such a term should improve the 
correlation between $\mathcal{I}_{100}$ and $\mathcal{I}_{857}$. However, the 
scatter plots shown in Figure \ref{fig:quad} make it clear that such a term 
dramatically improves the quality of the linear correlation between the 100 GHz
and 857 GHz channels. We tried re-running the fits at 143-545 GHz including the
$Q_p$ quadrupole term, but in all cases found the best-fit quadrupole to be 
negligible, and yield no substantial tightening of the correlation versus 857 
GHz.

% worth clarifying that, for quadrupole fit at 100 GHz, we still do the
% fit with uniform weights and iterative outlier rejection ?

>>>>

\begin{figure}
\begin{center}
\epsfig{file=dipole_all_100.eps, width=3.4in}
\caption{\label{fig:dip}  Scatter plots of \PLANCK~143, 217, 353, and 545 GHz 
versus \PLANCK~857 GHz. Left: before correcting for offset and residual Solar 
dipole. Right: after correcting or the best-fit offset and dipole amplitude, as
described in $\S$\ref{sec:zp}. The dashed red line shows the best-fit linear 
relationship in each case.}
\end{center}
\end{figure}

\begin{figure*}
\begin{center}
\epsfig{file=harm_100.eps, width=6.5in}
\caption{\label{fig:quad} Summary of low-order corrections at 100 GHz.}
\end{center}
\end{figure*}

@@

The need for additional low-order corrections beyond simple scalar offsets 
became evident upon inspecting the HFI maps at 100-545 GHz. In particular, we 
noticed the presence of a low-level dipole pattern, with an orientation 
consistent with that of the Solar dipole. Our strategy will be to 
simultaneously fit both this residual dipole and the zero-level offset 
amplitude for each band. To most precisely recover these amplitudes, it is 
necessary to have the highest available S/N in the independent variable of our 
regression. For this reason we have used \PLANCK~857 GHz as a reference for the
100-545 GHz bands, as opposed to the FDS99 predictions or H\,\textsc{i} data. 
In doing so, we assume \PLANCK~857 GHz contains no appreciable Solar dipole 
residual or other low-order problems. % grammar?

@@

We found that a dipole correction alone could not sufficiently rectify the 
\PLANCK~100 GHz map (see Figure \ref{fig:quad}). Therefore, for 100 GHz, we 
performed a modified version of the Equation \ref{equ:dip} fit, using the 
following model:

\begin{equation} \label{equ:harm}
\mathcal{I}_{100, p} = m\mathcal{I}_{857, p} + b + \sum_{l=1}^{4} \sum_{m=-l}^{l} a_{lm}Y_{l}^{m}(\theta_p, \phi_p)
\end{equation}

Where $Y_{l}^{m}$ are the real spherical harmonics, and the $a_{lm}$ are their 
corresponding real coefficients. The angle $\phi_p$ is taken simply to be 
$l_{gal, p}$ and $\theta_p$=$(90^{\circ}-b_{gal, p})$. Thus, we have replaced 
the Solar dipole term with a sum of 24 spherical harmonic templates, which, 
when multiplied by the best-fit $a_{lm}$ coefficients and subtracted from 
\PLANCK~100 GHz make the relation between 100 GHz and 857 GHz most tightly 
linear. Figure \ref{fig:quad} illustrates the improved correlation of 100 GHz 
vs. 857 GHz when including the spherical harmonic corrections relative to the 
dipole-only correction. The spherical harmonic decomposition of Equation 
\ref{equ:harm} did not improve the correlations at higher frequencies 
sufficiently to warrant replacing the dipole-only correction in those cases.
